---
title: "K-Nearest Neighbor (KNN) Regression on Boston Housing Dataset"
output:
  html_document:
    df_print: paged
---

### Load Packages
```{r echo=TRUE,results='hide'}
library(MASS)
library(MLmetrics)
library(caret)
```

Pada kasus regresi ini, akan digunakan data `Boston Housing` dengan rincian variabel sebagai berikut.

- `CRIM` : per capita crime rate by town
- `ZN` : proportion of residential land zoned for lots over 25,000 sq.ft.
- `INDUS` : proportion of non-retail business acres per town
- `CHAS` : Charles River dummy variable (1 if tract bounds river; 0 otherwise)
- `NOX` : nitric oxides concentration (parts per 10 million)
- `RM` : average number of rooms per dwelling
- `AGE` : proportion of owner-occupied units built prior to 1940
- `DIS` : weighted distances to five Boston employment centres
- `RAD` : index of accessibility to radial highways
- `TAX` : full-value property-tax rate per $10,000
- `PTRATIO` : pupil-teacher ratio by town
- `B` : 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town
- `LSTAT` : % lower status of the population
- `MEDV` : Median value of owner-occupied homes in $1000's

```{r}
boston <- MASS::Boston
head(boston)
```

### Data Scaling
*Scaling* data dilakukan untuk variabel prediktor yang bukan kategorik.
```{r}

x_scaled <- scale(boston[,-c(4,14)])[,]
boston_scaled <- cbind(x_scaled,boston[,c(4,14)])

head(boston_scaled)
```

### Data Partition
Data dibagi menjadi 90% data *training* dan 10% data *testing*.
```{r}
indexes <- createDataPartition(boston$medv,p = .9,list = F)
train <- boston_scaled[indexes,]
test <-boston_scaled[-indexes,]

train_x <- train[,-14]
train_y <- train[,14]

test_x <- test[,-14]
test_y <- test[,14]


```

### KNN Regression
Pembentukan model regresi KNN dengan k = 5.
```{r}
knnmodel <- knnreg(train_x,train_y,k=5)

pred_y <- predict(knnmodel,data.frame(test_x))

mape_test <- MAPE(pred_y,test_y)*100
rmse_test <- caret::RMSE(test_y, pred_y)

cat("MAPE: ",mape_test,"RMSE: ",rmse_test)
```

### Plot Actual vs. Predicted Data
```{r}
x = 1:length(test_y)
plot(x, test_y, col = "red", type = "l", lwd=2,
     main = "Boston Housing Test Data Prediction")
lines(x, pred_y, col = "blue", lwd=2)
legend("topright", title = "Data", legend = c("Actual", "Predicted"), 
       fill = c("red", "blue"), col = 2:3,  adj = c(0, 0.6))
grid() 
```
